\chapter{Analytification of a scheme}


\section{Toplogical story}


\subsection{Affine scheme}

% \subsubsection{The special case of polynomial ring}

% In this section we work explicitly with $R := \complex[X_{1},\dots, X_{n}]$.

Let $S$ be a finitely generated $\complex$-algebra so that $S \cong \complex[a_{1},\dots, a_{n}]$ for some $a_{i} \in S$. Thus there is a surjection $\theta: \complex[X_{1}, \dots, X_{n}] \to S$ defined by $X_{i} \mapsto a_{i}$. Thus, we have a morphism $\spec\theta$ of schemes of finite type over $\complex$ between $\spec S$ to $\spec{\complex[X_{1},\dots, X_{n}]}$. By \Cref{thm:morph-maps-closed-points-to-closed-points}, we know that $\specop\theta$ gives us a continuous map
\[
	%   We denote $\an{\left(\specop R\right)}$ to the space consisted of the closed points in $\specop R$ with the topology induced from $\complex^{n}$.
	\operatorname{MaxSpec}\theta: \operatorname{MaxSpec} S \to \operatorname{MaxSpec} \complex[X_{1},\dots, X_{n}],
\]

since $\theta$ is surjective, $\operatorname{MaxSpec}\theta$ is injective\footnote{being the restriction of the injective function $\specop \theta$}.

\begin{theorem}
	The set of closed points in $\specop{\complex[X_{1},\dots, X_{n}]}$ corresponds bijectively to $\complex^{n}$.

\end{theorem}
\begin{proof}
	By \Cref{thm:affine-scheme-closed-points-biject-algebra-hom}, the set of closed points
	bijects to $\complex$-algebra homomorphisms $\complex[X_{1}, \dots, X_{n}] \to \complex$. Thus we only need a bijection between $\complex$-algebra homomorphism $\complex[X_{1}, \dots, X_{n}] \to \complex$ and $\complex^{n}$:
	\begin{enumerate}
		\item Give a point $p := (a_{1},\dots, a_{n}) \in \complex^{n}$, we define $\phi_{a}: \complex[X_{1},\dots, X_{n}] \to \complex$ to be evaluation at the point $p$.

		\item Give a $\complex$-algebra homomorphism $\phi$, we take the point to be $(\phi(X_{1}, \dots, X_{n}))$.
	\end{enumerate}
\end{proof}

\begin{definition}[Analytification of topological spaces.]\label{def:analytification-topoloy}
	The complex topology of $\specop S$ is the subspace topology of $\complex^{n}$ via the injective map $\maxspecop \theta$. With the complex topology, we denote $\maxspecop S$ as $\an{\left(\specop S\right)}$ and, if $\phi : S \to S'$ is a $\complex$-algebra homorphism, we the induced map between $\an{\specop{S'}}$ and $\an{\specop{S}}$ as $\an{\specop \phi}$.
\end{definition}

Note that by now we do not know that $\an{\left(\specop S\right)}$ is independent from the choice of generators $\{a_{1},\dots, a_{n}\}$, we will enventually prove that this is true, but let's write $\an{\left(\specop S\right)}_{a_{i}}$ to stress the dependency.

\begin{theorem}
	If $S$, as $\complex$-algebras, is generated by both $a_{1},\dots, a_{n}$ and $b_{1},\dots,b_{m}$, we would have as topological spaces $\an{\left(\specop S\right)}_{a_{i}}$ and $\an{\left(\specop S\right)}_{b_{i}}$ are homeomophic.
\end{theorem}

\begin{proof}
	Let us abbreviate the polynomial rings $\complex[X_{1},\dots, X_{n}]$ as $R$ and $\complex[Y_{1},\dots, Y_{m}]$ as $R'$, then we have two surjective homomorphisms $\theta: R \to S$ and $\theta' : R' \to S$ such that $\theta(X_{i}) = a_{i}$ and $\theta'(Y_{i})=b_{i}$.

	It is sufficient, by symmetry, to prove topology induced by generators $b_{i}$'s is finer than that of $a_{i}$'s.

	Since $b_{i}$'s generate $S$ and $a_{i}$'s are in $S$, we can find $n$ polynomials $P_{i} \in R' = \complex[Y_{1},\dots, Y_{m}]$ such that $a_{i} = P_{i}(b_{1},\dots, b_{m})$. Thus we can define $\phi : R \to R'$ by $X_{i}\mapsto P_{i}(Y_{1},\dots, Y_{m})$ such that $\theta = \theta' \circ \phi$. Thus we have a commutative diagram (of plain functions)
	\begin{center}
		\begin{tikzcd}[column sep=large]
			{\an{\left(\specop{S}\right)}_{a_{i}}} \arrow{r}{\maxspecop\theta} \arrow[leftrightarrow]{d}[left]{=} & \complex^{n} \\
			{\an{\left(\specop{S}\right)}_{b_{i}}} \arrow{r}{\maxspecop{\theta'}} & \complex^{m} \arrow{u}[right]{\maxspecop{\phi}}
		\end{tikzcd}
	\end{center}

	It is sufficient to prove that $\maxspecop \phi$ is continuous, then since $\maxspecop \theta$, $\maxspecop \theta'$ and $\maxspecop \phi$ are all continuous, the identity function $\an{\left(\specop S\right)}_{a_{i}} \to \an{\left(\specop S\right)}_{b_{i}}$ is continuous.
	Consider a point $c = (c_{1},\dots, c_{m}) \in \complex^{m}$, then $\maxspecop\phi(c)$ is the point $\mathrm{eval}_{c} \circ \phi (X_{1},\dots, X_{n})$, i.e. $(c_{1},\dots, c_{m}) \mapsto (P_{1}(c_{1},\dots,c_{m}),\dots, P_{n}(c_{1},\dots,c_{m}))$. This is a map defined by polynomials, thus is continuous.
\end{proof}

Now we have proven that the complex topology is independent of generators, we can write $\an{\left(\specop S\right)}$ with a clear conscience.

\begin{lemma} Since $\an{\left(\specop S\right)}$, as a set, is just the set of closed points of $\specop S$, we have a function $\lambda: \an{\left(\specop S\right)} \hookrightarrow \specop S$. $\lambda$ is continuous where $\an{\left(\specop S\right)}$ is with complex topology while $\specop S$ is with the Zaraski toplogy.\label{thm:continuous-inclusion-complex-topology-affine}
\end{lemma}

\begin{proof}
	Let us choose a set of generators $a_{1},\dots, a_{n}$ and write $R := \complex[X_{1},\dots, X_{n}]$, then we would have the following commutative diagram:

	\begin{center}
		\begin{tikzcd}
			\an{\left(\specop{S}\right)} \arrow[hookrightarrow]{r}{\lambda_{S}} \arrow[red]{d}[left]{\mathrm{restriction~of}~\specop{\theta}}& \specop{S} \arrow{d}{\specop{\theta}} \\
			\an{\left(\specop{R}\right)} \arrow[hookrightarrow]{r}{\lambda_{R}} \arrow[red]{d}[left]{\sim} & \specop{R} \\
			\complex^{n} &
		\end{tikzcd},
	\end{center}
	where $\theta$ is the surjective $\complex$-algebra homomorphism $R \to S$.
	The red arrows are continuous, since they define the complex topology; $\specop \theta$ is continuous as well. To prove $\lambda_{S}$ is continuous, we only need to prove the special case $\lambda_{R}$ where $R = \complex[X_{1},\dots, X_{n}]$. Since $\specop R$ has a basis of basic open set $D(f)$, we only need to check that $D(f) \cap \an{\left(\specop R\right)}$ is open for any polynomial $f \in \complex[X_{1}, \dots, X_{n}]$, indeed the intersection is equal to $\{x \in \complex^{n}| f(x) \ne 0 \}$ thus open\footnote{$\mathfrak{p} \in D(f)$ if and only if $f \not\in \mathfrak{p}$. Hence $\mathfrak{m}$ is in the intersection if and onlyv if $\mathfrak{m}$ is equal to the kernel of evaluation map $\phi_{a}$ at some point $a$ and that $f$ is not in the kernel, in another word, $f(a) \ne 0$.}\footnote{should this be a separate lemma?}. %FIXME

\end{proof}

\begin{lemma}
	Let $a_{1},\dots, a_{n}$ be a set of generators of $S$ as $\complex$-algebra and $R$ be $\complex[X_{1},\dots,X_{n}]$ and $\theta : R \to S$ be the surjective map defined by $\theta(X_{i})=a_{i}$.
	The image of $\specop{\theta} : \an{\specop{S}} \to \an{\specop{R}}\cong\complex^{n}$ is
	\[
		V(\ker\theta):=\{(x_{1},\dots,x_{m})| f_{i}(x_{1},\dots,x_{n})=0\} = \{(x_{1},\dots,x_{m})| p(x_{1},\dots,x_{n})=0~\text{for all}~p\in \ker{\theta}\},
	\]
	where $f_{i}$ generates $\ker\theta$.
\end{lemma}
\begin{proof}
	$x = (x_{1},\dots,x_{n})\in\operatorname{image}\an{\specop\theta}$ if and only if $\psi_{x}$, evaluation at $x$, annilates the kernel of $\theta$ by \Cref{thm:maxspecop-alg-hom-annihilate}
\end{proof}

\begin{theorem}\label{thm:continuous-an-spec-complex-toplogy}
	Let $S$ and $S'$ be two finitely generated $\complex$-algebras and $\phi : S \to S'$ be a $\complex$-algebra homomorphism, the natural map $\an{\specop{\phi}} : \an{\specop{S'}} \to \an{\specop{S}}$ is continuous (in the complex topology)
	and compatible with the inclusion map, i.e.~the following diagram is commutative:
	\begin{center}
		\begin{tikzcd}[column sep = large]
			{\an{\specop{S'}}} \arrow{r}{\an{\specop{\phi}}} \arrow[hookrightarrow]{d} & {\an{\specop{S}}} \arrow[hookrightarrow]{d} \\
			{\specop{S'}} \arrow{r}{\specop{\phi}} & \specop{S}
		\end{tikzcd}
	\end{center}
\end{theorem}

\begin{proof}
	The commutativity is free.
	Let us choose generators $\{a_{1},\dots,a_{n}\}$'s for $S$ and $\{b_{1},\dots,a_{m}\}$'s for $S'$.
	Let us write the polynomial ring $\complex[X_{1},\dots,X_{n}]$ as $R$ and $\complex[Y_{1},\dots, Y_{m}]$ as $R'$. Then we have two surjective $\complex$-algebra homomorphisms $\theta: R \to S$ and $\theta' : R' \to S'$ as usual.
	Since $\{b_{i}\}$ generates $S'$, we can find polynomials $P_{i} \in R'$ such that $\phi(a_{i})= P_{i}(b_{1},\dots, b_{m})$. Then we can define a $\complex$-algebra homomorphism $\psi : R \to R'$ by $X_{i} \mapsto P_{i}(Y_{1},\dots, Y_{m})$ giving us the following commutative diagrams:
	\begin{center}
		\begin{tikzcd}[column sep = large]
			& & & {\complex^{n}} & {\complex^{m}} \\
			R \arrow{r}{\psi} \arrow{d}{\theta}& R' \arrow{d}{\theta'} & & {\an{\specop{R}}} \arrow[red]{u}{\sim} & {\an{\specop{R'}}} \arrow{l}[above]{\an{\specop{\psi}}} \arrow[red]{u}{\sim} \\
			S \arrow{r}{\phi} & S' & & {\an{\specop{S}}} \arrow[red]{u}{\an{\specop{\theta}}} & {\an{\specop{S'}}} \arrow[red]{u}{\specop{\theta'}} \arrow{l}{\an{\specop{\phi}}}
		\end{tikzcd}
	\end{center}
	The red arrows are continuous because they define the complex topology and $\an{\specop{\psi}}$ is continuous because it is defined by polynomial $\psi$. Thus $\an{\specop{\phi}}$ is continuous.
\end{proof}

\begin{corollary}
	If $S \to S'$ is an isomorphism of finite $\complex$-algebras, then $\an{\specop{S}}$ and $\an{\specop{S'}}$ are homeomorphic.
\end{corollary}

\begin{lemma}
	If $\phi: S \to S'$ is a surjective $\complex$-algebra homomorphism between two finite $\complex$-algebras, then $\an{\specop{\phi}} : \an{\specop{S'}} \to \an{\specop{S}}$ is an embedding.
\end{lemma}

\begin{proof}
	Let $\{a_{1},\dots, a_{n}\}'s$ be generators of $S$ and $R$ be the polynomial ring $\complex[X_{1},\dots, X_{n}]$. Then we have $\theta : R \to S$ such that $\theta(X_{i})=a_{i}$. The composition $R \stackrel{\theta}{\to} S \stackrel{\phi}{\to} S'$ is a surjection as well. Thus by taking $\an{\specop(-)}$ operation, we get
	\begin{center}
		\begin{tikzcd}[column sep=large]
			{\an{\specop{S'}}} \arrow{r}{\an{\specop{\phi}}} & {\an{\specop{S}}} \arrow{r}{\an{\specop{\theta}}} & {\an{\specop{R}}} \arrow{r}{\sim} & \complex^n.
		\end{tikzcd}
	\end{center}
	The whole composition is embedding because of independence of generators and $\an{\specop{\theta}}$ is an embedding as well, thus $\an{\specop{\phi}}$ is an embedding as well.
\end{proof}

\begin{lemma}
	Let us write $\complex[X_{1},\dots,X_{n}]$ as $R$ and let $f \in R$ be a polynomial, then the localization map $\alpha : R \to R_{f}$ induces an embedding $\an{\specop{R_{f}}} \hookrightarrow \an{\specop{R}}$.
\end{lemma}
%TODO: prove this
\begin{proof}
	TBD
\end{proof}

More generally, we have a corresponding lemma for arbitrary finite $\complex$-algebras.

\begin{lemma}
	If $S$ is a finite $\complex$-algebra and $f \in S$, then the localization map $\alpha : S \to S_{f}$ induces an embedding $\an{\specop{S_{f}}} \hookrightarrow \an{\specop{S}}$. In fact $\an{\specop{S_{f}}}$ is identified as the subset $D(f) \cap \specop{S}$ where $D(f)$ is the basic open set in $\specop{S}$.
\end{lemma}

% TODO
\begin{proof}
	TBD
\end{proof}

\subsection{Arbitrary scheme}

\begin{definition}[Complex Topology]
	Let $\schemeOf{X}$ be a scheme locally of finite type over $\complex$, let $\mathcal{I}$ be the collection of open immersions $\spec R \to X$ where $R$ is some finite $\complex$-algebra. Then the complex topology on the set of closed points $\max X$ is defined as the weak topology with respect to $\left\{\an{{\phi}} | (\phi, \phi^{*}) \in \mathcal{I}\right\}$ where $\an{\phi}$ is the restriction of $\phi$ to the subset of closed points. When we talk about complex toplogy, we write $\max{X}$ as $\an{X}$.
\end{definition}

% If $\Psi = (\psi, \psi^{*}) : \spec{R} \to X$ is an open immersion where $R$ is a finite $\complex$-algebra, by the definition of the complex topology, we know that $\an{{\psi}}$ is continuous, in fact it is an embedding as well where the image is open. Let $W \subseteq \an{\specop R}$ be an open subset, we need to show the image of $W$, $\an{\psi} W = \psi W$ is open in $\an{X}$. Let $S$ be an arbitrary finite $\complex$-algebra and $\Phi = (\phi, \phi^{*}) : \specop{S} \to \schemeOf{X}$ be an open immersion, we need to show that the inverse image of $\psi W$, ${\an{\phi}}^{-1}\psi W = \phi^{-1}\psi W$, is open in $\an{\specop S}$. Let $U$ be the image of $\phi^{-1}\psi W$ under $\an{\phi}$ and $V$ be the image under $\an{\psi}$. Then we have $\psi W \subseteq \max{V}$ (the closed points in $V$)

\begin{lemma}\label{thm:open-immersion-induced-embedding-complex-topology}
	Let $\schemeOf{X}$ be a scheme locally of finite type over $\complex$, $R$ be a finite $\complex$-algebra and $\Psi = (\psi, \psi^{*}) : \spec{R} \to \schemeOf{X}$ be an open immersion. Then $\an{\psi}$ is an embedding.
\end{lemma}

\begin{proof}
	TBD
\end{proof}

\begin{lemma}\label{thm:continuous-inclusion-complex-topology}
	Let $\lambda_{X} : \an{X} \hookrightarrow X$ be the inclusion map, then $\lambda_{X}$ is continuous.
\end{lemma}
\begin{proof}
	Let $x \in X$ and $U \cong \specop A$ be an open affine neighbourhood of $x$. Then we have the following commutative diagram:
	\begin{center}
		\begin{tikzcd}
			{\an{\specop{A}}} \arrow[hookrightarrow, red]{d} \arrow{r}{\iota_1} & {\an{X}} \arrow[hookrightarrow]{d}{\lambda_{X}} \\
			{\specop{A}} \arrow[hookrightarrow]{r} \arrow{r}{\iota_2} & X.
		\end{tikzcd}
	\end{center}
	The red arrow is continuous by \Cref{thm:continuous-inclusion-complex-topology-affine}; $\iota_{1}$ is continuous by \Cref{thm:open-immersion-induced-embedding-complex-topology}; $\iota_{2}$ is an open embedding by hypothesis. Thus $\lambda_{X}$ is continuous as well.
\end{proof}

\begin{lemma}
	Let $\Phi = (\phi, \phi^{*}) : \schemeOf{X} \to \schemeOf{Y}$ be a morphism of schemes locally of finite type over $\complex$, then $\an{\phi} : \an{X} \to \an{Y}$ is continuous.
\end{lemma}
\begin{proof}
	Let $x \in X$ and $U \cong \specop A \subseteq X$ and $V \cong \specop B \subseteq Y$ such that $\phi U \subseteq V$ be affine neighbourhoods around $x$ and $\phi(x)$\footnote{This is possible by definition of being locally finite.}. Then $\Phi|_{U} : \spec A \to \spec B$ is induced by a $\complex$-algebra homomorphism $\alpha: B \to A$, thus we have the following two commutative squares:
	\begin{center}
		\begin{tikzcd}[column sep=large]
			{\spec{A}} \arrow{r}{\spec{\alpha}} \arrow[hookrightarrow]{d} & {\spec{B}} \arrow[hookrightarrow]{d} & {\an{\specop{A}}} \arrow[hookrightarrow, red]{d} \arrow{r}{\an{\specop{\alpha}}} & {\an{\specop{B}}} \arrow[hookrightarrow, red]{d}\\
			{\schemeOf{X}} \arrow{r}{\Phi} & {\schemeOf{Y}} & {\an{X}} \arrow{r}{\an{\phi}} & \an{Y}.
		\end{tikzcd}
	\end{center}
	where the red arrows are continuous by \Cref{thm:continuous-inclusion-complex-topology} and $\an{\specop\alpha}$ is continuous by \Cref{thm:continuous-an-spec-complex-toplogy}. Thus $\an{\phi}$ is continuous as well.
\end{proof}

\begin{corollary}
	Let $\Phi : \schemeOf{X} \to \schemeOf{Y}$ be an open immersion of schemes locally of finite type over $\complex$, then $\an{\phi}$ is an embedding of $\an{X}$ into $\an{Y}$.
\end{corollary}
\begin{proof}
	TBD
\end{proof}

Here are two easy consequences:
\begin{corollary}
	Given two morphisms among schemes locally of finite type over $\complex$
	\begin{center}
		\begin{tikzcd}
			{\schemeOf{X}} \arrow{r}{(\phi, \phi^{*})} & {\schemeOf{Y}} \arrow{r}{(\psi, \psi^{*})} & {\schemeOf{Z}},
		\end{tikzcd}
	\end{center}
	we have $\an{\psi\circ\phi} = \an{\psi} \circ \an{\phi}$
\end{corollary}
\begin{proof}
	Restriction of composition is composition of restriction.
\end{proof}

\begin{corollary}
	Let $\Phi = (\phi, \phi^{*}) : \schemeOf{X} \to \schemeOf{Y}$ be a morphism of schemes locally of finite type over $\complex$, we have
	\begin{center}
		\begin{tikzcd}
			{\an{X}} \arrow{r}{{\an{\phi}}} \arrow[hookrightarrow]{d} & {\an{Y}} \arrow[hookrightarrow]{d} \\
			X \arrow{r}{\phi} & Y
		\end{tikzcd}
	\end{center}
\end{corollary}


\section{Sheaf side}

In previous section, we have showed that for any scheme $\schemeOf{X}$ locally of finite type over $\complex$, we can make a topological space $\an{X}$ with the complex topology. In this section, we aim to make a sheaf $\an{\mathcal{O}_{X}}$ on $\an{X}$. We will consider the affine cases $\spec{S}$ where $S$ is a finite $\complex$-algebra by choosing generators; then we prove that the construction does not dependent on the choice of generators; then we glue everything together.

\subsection{Affine schemes}
Let $S$ be a finite $\complex$-algebra, we choose generators $a_{1},\dots, a_{n}$ and write $\complex[X_{1},\dots,X_{n}]$ as $R$. Thus we have a surjective $\complex$-algebra homomorphism $\theta: R \to S$ such that $\theta(X_{i}) = a_{i}$. Then $\ker\theta$ is finitely generated as well, say by $f_{1},\dots,f_{m}$.
Note that the image of $\an{\specop\theta}:\an{\specop S}\to\an{\specop\complex[X_{1},\dots, X_{n}]}\cong \complex^{n}$, which we often just write as $\an{\specop\theta}$ as well, is in bijection with $V(\ker\theta) := \{x \in \complex^{n}\mid f_{i}(x) = 0~\text{for all}~i\}$\footnote{by \Cref{thm:maxspecop-alg-hom-annihilate}}; hence is closed in $\complex^{n}$ because its the intersection of inverse images of the singleton set $\{0\}$.

We do constructions using $f_{1},\dots, f_{m}$, so everything depends on the choice of $a_{1},\dots,a_{n}$. In this section, we also denote the sheaf of holomorphic function as $\mathcal{Hol}$ where $\sections{\mathcal{Hol}}{U} := \{f : U \to \complex | f~\text{is holomorphic}\}$ for any open subset $U \subseteq \complex^{n}$.

We use a specialized basis of topology on $\complex^{n}$.
\begin{definition}[Generalized polydiscs]\label{def:generalized-polydisc}
  A generalized polydisc
  \[\Delta(g_{1},\dots,g_{l}; w_{1},\dots, w_{l}; r_{1},\dots, r_{l})\]
  is the set $\left\{x \in \complex^{n}| \left|g_{i}(x) - w_{i}\right| < r_{i}~\text{for all}~i = 1,\dots,l \right\}$ where each $g_{i} \in \complex[X_{1}\dots,X_{n}]$ is a polynomial of $n$ variables, $w := (w_{1},\dots, w_{n}) \in \complex^{l}$ is a point and $r := (r_{1},\dots,r_{l})\in\mathbb{R}^{l}_{\ge0}$ are all non-negative. We call $w$ the center of the polydisc and $r$  the polyradius\footnote{Different polydiscs can have different $l$}.
\end{definition}

\begin{remark}
	Traditionally, a polydisc $\Delta(w_{1},\dots, w_{l}; r_{1},\dots,r_{l}) := \{x \in \complex^{l}| \left|w_{i}-r_{i}\right| < r_{i}\}\}$ is the special case $\Delta(X_{1},\dots,X_{n};w_{1},\dots,w_{n}; r_{1},\dots, r_{n})$. For a generalized polydisc $\Delta(g; w; r)$, we have a map $g : \complex^{n}\to\complex^{l}$ defined by $x \mapsto (g_{1}(x),\dots,g_{l}(x))$. Note that $\Delta(g; w; r)$ is equal to $g^{-1}\Delta(w; r)$, the inverse image of the usual polydisc. So generalized polydiscs are exactly the inverse image of usual polydiscs by some polynomial map.
\end{remark}

\begin{lemma}[Basis of generalized polydiscs]
	All generalized polydiscs form a topological basis of $\complex^{n}$.
\end{lemma}
\begin{proof}
	\begin{itemize}
		\item Every open set is a union of generalized polydiscs. Just take small polyradius and $g_{i} = X_{i}$.
		\item Intersection of two generalized polydiscs is a generalized polydisc. Consider $\Delta(g; w; r)$ and $\Delta(g'; w'; r')$. The idea is the following: $\Delta(g; w; r)$ is $g^{-1}\Delta(w; r)$ and $\Delta(g'; w'; r') = {g'}^{-1}\Delta(g'; w; r'))$, and $(g, g'): \complex^{n} \to \complex^{l}\times\complex^{l'}\cong \complex^{l + l'}$ is a polynomial map, call it $G$. Since $\Delta(w; r) \times \Delta(w'; r')$ is a usual polydisc, its inverse image under $G$ is a generalized polydiscs and is equal to the intersection of the original generalized polydiscs.
	\end{itemize}
\end{proof}

The following terminology is nonstandard.
\begin{definition}[Preanalytification of sheaves.]\label{def:preanalytification-sheaf}
  We have a sheaf $\mathcal{O}^{\mathsf{pre}}$ on $\complex^{n}$ is defined to be the cokernel sheaf of the following exact sequence:
	\begin{center}
		\begin{tikzcd}
			{\mathcal{Hol}^{\oplus m}} \arrow{r} & {\mathcal{Hol}} \arrow{r} & {\mathcal{O}^{\mathsf{pre}}} \arrow{r} & 0,
		\end{tikzcd}
	\end{center}
	where the first arrow, on $U$, is given by $(a_{1},\dots,a_{m}) \mapsto f_{1}|_{U}\smul a_{1}+\cdots+f_{m}|_{U}\smul a_{m}$ where $a_{i} \in \sections{\mathcal{Hol}}{U}$ and $f_{i}$ generates $\ker\theta$
\end{definition}

\begin{lemma}
	On generalized polydiscs $\Delta_{1} \subseteq \Delta_{2}$, $\sections{\mathcal{O}^{\mathsf{pre}}}{\Delta_{1}}$ is isomorphic to \[\quotient{\sections{\mathcal{Hol}}{\Delta_{1}}}{\ker\theta\smul\sections{\mathcal{Hol}}{\Delta_{1}}}\] and the restriction map $\sections{{\mathcal{O}^{\mathsf{pre}}}}{\Delta_{2}} \to \sections{{\mathcal{O}^{\mathsf{pre}}}}{\Delta_{1}}$ is the restriction map
	\[
		\mathrm{res} :
		\quotient{\sections{\mathcal{Hol}}{\Delta_{2}}}{\ker\theta\smul\sections{\mathcal{Hol}}{\Delta_{2}}} \to
		\quotient{\sections{\mathcal{Hol}}{\Delta_{1}}}{\ker\theta\smul\sections{\mathcal{Hol}}{\Delta_{1}}}
	\]
	defined by $[f] \mapsto [f\mid_{U}]$.
\end{lemma}
\begin{proof}
	This lemma is going to be hard. Uses coherent analytic sheaves, Cartan's Theorem, Stein manifold, etc. The author of \cite[page~108]{neeman2007algebraic} tells us to look at \cite[page~136, definition 2; page 243, theorem 2]{gunning2022analytic}.
\end{proof}

% % {\bf The following might to be a good idea in formalisation.} I will define $\an{\mathcal{O}_{X}}$ by defining it only on basis, then extend it. For arbitrary open subsets $U \subseteq V$, we have the following
% % \begin{center}
% %   \begin{tikzcd}
% %    \complex[X_{1},\dots, X_{n}] \arrow[hookrightarrow, red]{r} & \sections(\mathcal{Hol}, \complex^n) \arrow[red]{r}{\mathrm{res}} & \sections(\mathcal{Hol}, U) \arrow[two heads]{r} & \quotient{\sections(\mathcal{Hol}, U)}{\ker\theta\smul\sections(\mathcal{Hol}, U)},
% %   \end{tikzcd}
% % \end{center}
% % where the first arrow is an inclusion since all polynomials are holomorphic; the second arrow is the restriction map of $\mathcal{H}$. Here $\ker\theta\smul \sections(\mathcal{Hol}, U)$ is the image of $\ker\theta$ of the composition of the two read arrows.
% % We can also define the restriction of  Unfortunately, this is not a sheaf on $\complex^{n}$, but it is indeed a sheaf on the basis of generalized polydiscs of $\complex^{n}$

\begin{lemma}\label{thm:trivial-preanalytification-sheaf-on-generalized-polydisc-outside}
  Let $x$ be a point not in $\an{\specop{S}}$, in another word, $x \in \complex^{n} - \an{\specop{S}}$.
  There is an open subset $x \in U \subseteq \complex^{n}$ such that for any generalized polydiscs $\Delta \subseteq U$, we have $\sections{\mathcal{O}^{\mathsf{pre}}}{\Delta} = 0$.
\end{lemma}
\begin{proof}
  By \Cref{thm:maxspecop-alg-hom-annihilate}, $x$ is not in the image of $\an{\specop{S}}$ precisely when at least one of the $f_{i}(x) \ne 0$. Say it's the first one. Then, there is some open neighbourhood $U$ around $x$ such that $f_{1}\mid_{U}$ is nowhere zero, i.e.\ invertible. Thus for any generalized polydisc $\Delta \subseteq U$, we have that the ideal $\ker\theta\smul\sections{\mathcal{Hol}}U$ is everything so that $\sections{\mathcal{O}^{pre}}{\Delta}\cong\quotient{\sections{\mathcal{Hol}}{\Delta}}{\ker\theta\smul\sections{\mathcal{Hol}}{\Delta}}$ is trivial.
\end{proof}
\begin{corollary}[$\mathcal{O}^{\mathsf{pre}}$ is supported in $\an{\specop{S}}$]\label{thm:trivial-preanalytification-sheaf-on-outside-open-set}
\uses{thm:trivial-preanalytification-sheaf-on-generalized-polydisc-outside}
  Let $V \subseteq \complex^{n}-\an{\specop S}$ be an open set in $\complex^{n}$, then the sections of $\mathcal{O}^{\mathsf{pre}}$ on $V$ is trivial.
\end{corollary}
\begin{proof}
  Let $\sigma \in \sections{\mathcal{O}^{\mathsf{pre}}}{V}$, we want to show that $\sigma(x) = 0$ for all $x \in V$. By \Cref{thm:trivial-preanalytification-sheaf-on-generalized-polydisc-outside}, there exists some open neightbourhood $x \in U \subseteq V$\footnote{if $U$ is not a subset of $V$, then use $U \cap V$} such that
  sections of $\mathcal{O}^{\mathsf{pre}}$ on any generalized polydiscs contained in $U$ is trivial. Thus we can cover $V$ by a family of generalized polydiscs $\Delta_{i}$ such that $\sigma\mid_{\Delta_{i}}$ are all zero; therefore by sheaf axioms, $\sigma$ is zero.
\end{proof}

\begin{corollary}
\uses{thm:trivial-preanalytification-sheaf-on-outside-open-set}
  Let $V\subseteq\complex^{n}$ be an open subset then we have an isomorphism
  \[
\sections{\mathcal{O}^{\mathsf{pre}}}{V \cup (\complex^{n} - \an{\specop S})} \cong \sections{\mathcal{O}^{\mathsf{pre}}}{V}
  \]
\end{corollary}
\begin{proof}
  Write $A := \complex^{n}-\an{\specop S}$, we need to prove the restriction map from $V \cup A$ to $V$ is both injective and surjective.
  \begin{itemize}
	\item Injectivity: suppose a section $\sigma \in \sections{\mathcal{O}^{\mathsf{pre}}}{V \cup A}$ is in the kernel of the restriction map, in another word, $\sigma\mid_{V}$ is zero. Then if we cover $V \cup A$ by $V$ and $A$, we would know that $\sigma\mid_{A}$ is zero as well\footnote{by \Cref{thm:trivial-preanalytification-sheaf-on-outside-open-set} and that $A$ is open}, so by sheaf axiom, $\sigma$ is zero.
	\item Surjectivity: let $\sigma$ be a section in $\sections{\mathcal{O}^{\mathsf{pre}}}{V}$, then we can glue $\sigma$ and $0 \in \sections{\mathcal{O}^{\mathsf{pre}}}{A}$ because $\sigma\mid_{V \cap A}$ must be zero, since $\sections{\mathcal{O}^{\mathsf{pre}}}{V\cap A}$ is trivial by \Cref{thm:trivial-preanalytification-sheaf-on-outside-open-set}.
  \end{itemize}
\end{proof}

\begin{definition}[Analytification of sheaf]\label{def:analytification-sheaf-affine}
  The analytification $\an{\sheafOfSpec{S}}$ of $\sheafOfSpec{S}$ is a presheaf on $\an{\specop S}$ defined by the following:
  \begin{itemize}
	\item For any open set $U \subseteq \an{\specop S}$, we define the sections $\sections{\an{\sheafOfSpec{S}}}{U}$ to be
		  $$\sections{\mathcal{O}^{\mathsf{pre}}}{U \cup \left(\complex^{n}-\an{\specop S}\right)}.$$
	\item For any open sets $U \subseteq V \subseteq \an{\specop{S}}$, we define the restriction map of $\an{\sheafOfSpec{S}}$ from $V$ to $U$ is the restriction map of $\mathcal{O}^{\mathsf{pre}}$ from $V \cup \left(\complex^{n}-\an{\specop S}\right)$ to $U \cup \left(\complex^{n}-\an{\specop{S}}\right)$.
  \end{itemize}
This defines a presheaf, the satisfaction of sheaf axioms are essentially from that of $\mathcal{O}^{\mathsf{pre}}$.
\end{definition}

\begin{remark}[Independence of the generators $f_{1},\dots, f_{m}$] Though the definition of $\mathcal{O}^{\mathsf{pre}}$ explicity uses $f_{i}$'s, we see that on the basis of generalized polydiscs, the sections on a generalized polydisc is $\quotient{\sections{\mathcal{Hol}}{\Delta}}{\ker\theta\smul\sections{\mathcal{Hol}}{\Delta}}$ which does not mention any generators. Since two sheaves are isomorphic if their sections on a basis are isomorphic, we must conclude that $\mathcal{O}^{\mathsf{pre}}$ is independent of the choice of $f_{1},\dots,f_{m}$ as well. But we don't know yet if the construction is independent from the choice of $a_{1},\dots, a_{m}$.
\end{remark}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../content"
%%% End:
